---
title: "UKR NTL"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data

```{r}
library(exactextractr)
library(raster)
library(terra)
library(sf)
library(tidyverse )
library(ggridges)
library(here)
source("R/vnp46A_to_wgs84.R")
```


```{r}
# https://db.rstudio.com/databases/postgresql/
con <- DBI::dbConnect(RPostgres::Postgres(),
                      # Driver   = "PostgreSQL Driver",
                      # Server   = "postgres",
                      dbname = "impact_db",
                      user      = rstudioapi::askForPassword("Database user"),
                      password      = rstudioapi::askForPassword("Database password"),
                      port     = 5432)

DBI::dbListTables(con) |> dput()

admin4_oi <-  "Yavoriv"
admin4_poi <- c("UA4614011001")
adm4 <- st_read(dsn = con,"ukr_admbnda_adm4_sspe_20220114") 
adm1 <- st_read(dsn = con,"ukr_admbnda_adm1_sspe_20220114") 
ocha <- st_read(dsn = con,"ukr_adm4_ocha_1") 
colnames(ocha) <- colnames(ocha) |> str_remove(pattern = "_1$")

# st_write(obj = ocha,dsn = con,layer = "ukr_adm4_ocha")
?DBI::dbWriteTable(conn = con,name = )
ocha
adm1_donetska <-  adm1 |> 
  filter(admin1Name_en=="Donetska")

# adm4$admin4Name_en
aoi <-  adm4 |> 
  filter(admin4Pcode ==admin4_poi) |> 
  janitor::clean_names() 

adm4 |> 
  filter(str_detect(admin4Name_en,"Pisoc")) |> 
  select(matches("^admin\\d+.[[eP]+."))

```

```{r}

h5_filenames <- list.files("raster/h5/",pattern = "\\.h5$")
h5_paths <- list.files("raster/h5/", full.names = T,pattern = "\\.h5$")


dnbs<- h5_paths |> 
  map(~vnp46A_to_wgs84(path =.x)) |> 
  set_names(h5_filenames)

# subset to just main band of interest for speed mosaicing
dnb_radiance <- dnbs |> 
  map(~.x |> subset("DNB_At_Sensor_Radiance_500m"))

# dir.create("raster/geotiff/mosaics/20220329_mosaics")
if(write_batch){
  ntl_rad_by_doy <-  mosaic_vnp46a_by_doy(dnb_radiance,output = "raster/geotiff/mosaics/20220329_mosaics")
}

ntl_rad_by_doy$`043`
as.Date(as.numeric(83), origin = '2021-12-31')

if(adm=="mariupol"){
  # feb 14  & March 13
  mariupol_before<- terra::crop(x = ntl_rad_by_doy$`043`,y=st_bbox(adm1_donetska) |> st_as_sfc())
  mariupol_after<- terra::crop(x = ntl_rad_by_doy$`072`,y=st_bbox(adm1_donetska) |> st_as_sfc())
  as.Date(as.numeric(43), origin = '2021-12-31')
  as.Date(as.numeric(72), origin = '2021-12-31')
  # dir.create("20220315_ukr_kyiv_viirs_ntl/raster_composites/mariupol_before_after")
  terra::writeRaster(mariupol_before,"20220315_ukr_kyiv_viirs_ntl/raster_composites/mariupol_before_after/VNP46A1.20220212.wgs84.tiff" )
  terra::writeRaster(mariupol_after,"20220315_ukr_kyiv_viirs_ntl/raster_composites/mariupol_before_after/VNP46A1.20220313.wgs84.tiff" )
 
    
    
  
}
ntl_rad_by_doy <-  mosaic_vnp46a_by_doy(dnb_radiance)



```

```{r}
dnbs[[1]] |> names("QF_Cloud_Mask" )
# subset to just main band of interest for speed mosaicing
dnb_radiance <- dnbs |> 
  map(~.x |> subset("QF_Cloud_Mask" ))
dir.create("raster/geotiff/mosaics/cloud_test")
mosaic_vnp46a_by_doy(dnb_radiance,output = "raster/geotiff/mosaics/cloud_test")
```






ntl_rad_by_doy <-  mosaic_vnp46a_by_doy(dnb_radiance)



feb27<- terra::crop(x = ntl_rad_by_doy$`058`,y=st_bbox(adm4) |> st_as_sfc())
feb28<- terra::crop(x = ntl_rad_by_doy$`059`,y=st_bbox(adm4) |> st_as_sfc())
# terra::writeRaster(feb27,"feb27_wtf.tiff")
terra::writeRaster(feb27,"feb27_wtf.tiff",overwrite=T)
terra::writeRaster(feb28,"feb28_wtf.tiff",overwrite=T)
plot(feb27,min=0, max=1000)
terra::sprc
terra_col<- ?terra::src(dnbs_by_doy$`073`)

terra::mosaic(terra_col)
terra_col |> attr()
do.call(terra::mosaic,dnbs_by_doy$`073`)


dnbs |> length()
dnb_march14<- terra::mosaic(dnbs[[11]]["DNB_At_Sensor_Radiance_500m"],dnbs[[12]]["DNB_At_Sensor_Radiance_500m"])
dnb_feb13<- terra::mosaic(dnbs[[1]]["DNB_At_Sensor_Radiance_500m"],dnbs[[2]]["DNB_At_Sensor_Radiance_500m"])
terra::writeRaster(dnb_march14,"raster/geotiff/VNP46A1_NRT.A2022073_dnb_wgs84_mosaic.tiff")
terra::writeRaster(dnb_feb13,"raster/geotiff/VNP46A1_NRT.A2022044_dnb_wgs84_mosaic.tiff")

names(dnbs)
names(dnbs[[1]])
```



finally morning of 20220-03-15 brdf adjusted vnp46a2 came out-- okay it is terrible.
  
cities

```{r}


```


```{r postgres}

# https://db.rstudio.com/databases/postgresql/
con <- DBI::dbConnect(RPostgres::Postgres(),
                      # Driver   = "PostgreSQL Driver",
                      # Server   = "postgres",
                      dbname = "impact_db",
                      user      = rstudioapi::askForPassword("Database user"),
                      password      = rstudioapi::askForPassword("Database password"),
                      port     = 5432)

DBI::dbListTables(con)

admin4_oi <-  "Yavoriv"
admin4_poi <- c("UA4614011001")
adm4 <- st_read(dsn = con,"ukr_admbnda_adm4_sspe_20220114") 


# adm4$admin4Name_en
aoi <-  adm4 |> 
  filter(admin4Pcode ==admin4_poi) |> 
  janitor::clean_names() 



# aoi <- st_read(dsn = con,"ukr_cities_of_interest_v1") |> select(-path)

# this will change
# ntl_raster<- raster(raster_path)


```

```{r}



mar14_dnb_aoi <- exactextractr::exact_extract(dnb_march14, aoi,include_cols=c("admin4pcode",
                                                                            "admin4name_en",
                                                                            "admin3name_en",
                                                                            "admin2name_en",
                                                                            "admin1name_en")) |> 
  bind_rows() |> 
  mutate(date= "2022-03-14")

feb13_dnb_aoi <- exactextractr::exact_extract(dnb_feb13, aoi,include_cols=c("admin4pcode",
                                                                            "admin4name_en",
                                                                            "admin3name_en",
                                                                            "admin2name_en",
                                                                            "admin1name_en")) |> 
  bind_rows() |> 
  mutate(date= "2022-02-14")


  



before_after <-  bind_rows(mar14_dnb_aoi,feb13_dnb_aoi)
before_after |> 
  ggplot(aes(x = value, y = date)) +
  geom_density_ridges(rel_min_height = 0.01, scale=3, alpha = 0.7)+
  labs(x="DNB Value at Sensor",y="",title = "Yavoriv: Distribution of light pixel values",subtitle = "March 14 vs Feb 13 2022")
```


check out quality flags
```{r}
dnbs[[1]] |> names()
feb13_dnb_qf<- terra::mosaic(dnbs[[1]]["QF_DNB"  ],dnbs[[2]]["QF_DNB"  ])

feb13_dnb_aoi <- exactextractr::exact_extract(feb13_dnb_qf, aoi,include_cols=c("admin4pcode",
                                                                            "admin4name_en",
                                                                            "admin3name_en",
                                                                            "admin2name_en",
                                                                            "admin1name_en")) |> 
  bind_rows() |> 
  mutate(date= "2022-02-14")
# dnbs[[1]] |> names()
feb13_dnb_cloud_qf<- terra::mosaic(dnbs[[1]]["QF_Cloud_Mask" ],dnbs[[2]]["QF_Cloud_Mask"])

feb13_dnb_cloud_aoi <- exactextractr::exact_extract(feb13_dnb_cloud_qf, aoi,include_cols=c("admin4pcode",
                                                                            "admin4name_en",
                                                                            "admin3name_en",
                                                                            "admin2name_en",
                                                                            "admin1name_en")) |> 
  bind_rows() |> 
  mutate(date= "2022-02-14")
feb13_dnb_cloud_aoi$value





feb13_dnb_and_qfs<- terra::mosaic(dnbs[[1]][[c("DNB_At_Sensor_Radiance_500m","QF_DNB" ,"QF_Cloud_Mask" ) ]],
                                  dnbs[[2]][[c("DNB_At_Sensor_Radiance_500m","QF_DNB" ,"QF_Cloud_Mask" ) ]]
)

#     terra::writeRaster(feb13_dnb_and_qfs,"raster/geotiff/feb13_cloud_qf.tiff")
                                  
dnbs[[2]][[c( "QF_Cloud_Mask" )]] |> hist()

base::bitwShiftL(50)
```


run zonal stats
```{r}

# probably makes sense to buffer aoi polygons

ntl_values_aoi <- exactextractr::exact_extract(ntl_raster, aoi,include_cols=c("admin4pcode",
                                                                            "admin4name_en",
                                                                            "admin3name_en",
                                                                            "admin2name_en",
                                                                            "admin1name_en"))

ntl_values_aoi_df <- bind_rows(ntl_values_aoi)

```


plot distributions

```{r}

ntl_values_aoi_df <- ntl_values_aoi_df |> filter(value<1000)
ggplot(ntl_values_aoi_df, aes(x = value, y = admin4name_en)) +
  geom_density_ridges(rel_min_height = 0.01, scale=3, alpha = 0.7)





```




## BRDF Attempt
- try on latest BRDF corrected imagery
```{r ,eval=F}

h5_filenames <- list.files("raster/46A2_h5//")
h5_paths <- list.files("raster/46A2_h5/", full.names = T)

dnbs<- h5_paths |> 
  map(~vnp46A_to_wgs84(path =.x)) |> 
  set_names(h5_filenames)
names(dnbs[[1]])

"DNB_BRDF-Corrected_NTL" 

brdf_corrected <-  dnbs |> map(~.x[["DNB_BRDF-Corrected_NTL"]])

brdf_corrected_mosaic <-  terra::mosaic(brdf_corrected[[1]],brdf_corrected[[2]],brdf_corrected[[3]],brdf_corrected[[4]],brdf_corrected[[5]],brdf_corrected[[6]])
terra::writeRaster(brdf_corrected_mosaic,"VNP46A2.A2022065_brdf_wgs84_mosaic.tiff")

```

should really write a function to parse the days and mosaic

```{r}

vnp46A_mosaic_by_doy <- function(path){
  #regext to get between second two dots
  # then take last 3 digits
  
  
}

```



